NHF1 Deamination Sequence and Position Figure Generation

### 2022-05-20 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
I should have made more intermediate commits
- Added options for filtering (e.g. TGG filtering) as knitting parameters and interactive input.
- Changed mismatch frequency peak calling process to utilize individual positions' z-scores.
- Integrated mismatch frequency z-scores into mismatch frequency plotting.
- Lots of other bugfixes and tweaks. Hopefully the whole project is in a steady-state right now.

---
title: "NHF1 Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

@@

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i]
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i]
      ))
  }
}
```

@@

for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    fwrite(CPDMismatchData[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
             repitition = names(CPDMismatchData)[i]
           ))
  }
}

for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    fwrite(sixFourMismatchData[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
             repitition = names(sixFourMismatchData)[i]
           ))
  }
}
```

@@

for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    fwrite(CPDGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
             strandPolarity = names(CPDGroupedStats[[i]])[j]
           ))
  }
}

for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    fwrite(sixFourGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
             strandPolarity = names(sixFourGroupedStats[[i]])[j]
           ))
  }
}
```

>>>>

---
title: "NHF1 Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
expansionOffset = 0

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

@@

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering
      ))
  }
}
```

@@

# Write the simplified mismatch data
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    fwrite(CPDMismatchData[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
             repitition = names(CPDMismatchData)[i], filtering = filtering
           ))
  }
}

for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    fwrite(sixFourMismatchData[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
             repitition = names(sixFourMismatchData)[i], filtering = filtering
           ))
  }
}
```

```{r generate_and_write_mismatch_frequency_z-scores}
# Don't forget to subset by C>T mismatches!
CPDMMFreqZScores = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) {
    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset)
  }
))
sixFourMMFreqZScores = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) {
    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset)
  }
))

for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    fwrite(CPDMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}

for (i in seq_along(sixFourMMFreqZScores)) {
  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
    fwrite(sixFourMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}
```

@@

for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    fwrite(CPDGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
             strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering
           ))
  }
}

for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    fwrite(sixFourGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
             strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering
           ))
  }
}
```

### 2022-05-20 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
I should have made more intermediate commits
- Added options for filtering (e.g. TGG filtering) as knitting parameters and interactive input.
- Changed mismatch frequency peak calling process to utilize individual positions' z-scores.
- Integrated mismatch frequency z-scores into mismatch frequency plotting.
- Lots of other bugfixes and tweaks. Hopefully the whole project is in a steady-state right now.

---
title: "NHF1 Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output",cellType,
                                           "deamination_sequence_and_position_figures"),
                                 .Platform$file.sep))
if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

@@

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in seq_along(CPDMismatchData)) {
  for (j in seq_along(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i]
    ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMismatchData)) {
  for (j in seq_along(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i]
    ))
  }
}
```

```{r CPD_mismatch_type_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchTypeFrequencies(CPDMismatchData[[i]][[j]],
                                title = paste("CPD", names(CPDMismatchData)[i], 
                                              names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"))
  }
}
```

```{r 6-4_mismatch_type_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
                                title = paste("6-4", names(sixFourMismatchData)[i], 
                                              names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"))
  }
}
```

```{r CPD_mismatch_pos_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}
```

```{r 6-4_mismatch_pos_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("6-4", names(sixFourMismatchData)[i], 
                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("6-4", names(sixFourMismatchData)[i], 
                                                  names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}
```

```{r CPD_trinucleotide_context_analysis}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotTrinucleotideContext(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                             title = paste("CPD", names(CPDMismatchData)[i], names(CPDMismatchData[[i]])[j],
                                           "C>T Mismatch Trinuc Context"))
  }
}
```

```{r 6-4_trinucleotide_context_analysis}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotTrinucleotideContext(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                             title = paste("6-4", names(sixFourMismatchData)[i], names(sixFourMismatchData[[i]])[j],
                                           "C>T Mismatch Trinuc Context"))
  }
}
```

```{r CPD_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
                                         title = "CPD C>T Mismatch Pos Freq Rep1")
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
                                         title = "CPD C>T Mismatch Pos Freq Rep2")
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
                                         title = "CPD C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
                                         title = "CPD C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
```

```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
                                         title = "6-4 C>T Mismatch Pos Freq Rep1")
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
                                         title = "6-4 C>T Mismatch Pos Freq Rep2")
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
                                         title = "6-4 C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
                                         title = "6-4 C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
```

```{r read_mismatch_position_statistics}
CPDGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                       rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    CPDGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
      strandPolarity = names(CPDGroupedStats[[i]])[j]
    ))
  }
}

sixFourGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                           rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    sixFourGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
      strandPolarity = names(sixFourGroupedStats[[i]])[j]
    ))
  }
}
```

```{r CPD_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
                         title = "CPD C>T Mismatch Pos Diff Rep1",
                         xAxisBreaks = c(23:31))
plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
                         title = "CPD C>T Mismatch Pos Diff Rep2",
                         xAxisBreaks = c(23:31))
```

```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
                         title = "6-4 C>T Mismatch Pos Diff Rep1",
                         xAxisBreaks = c(23:31))
plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
                         title = "6-4 C>T Mismatch Pos Diff Rep2",
                         xAxisBreaks = c(23:31))
```

>>>>

---
title: "NHF1 Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (length(filtering) > 0) {
  titleCaseFiltering = tools::toTitleCase(gsub('_', ' ', filtering))
} else titleCaseFiltering = character()

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output",cellType,
                                           paste(c(filtering,"deamination_sequence_and_position_figures"), collapse = '_')),
                                 .Platform$file.sep))

@@

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in seq_along(CPDMismatchData)) {
  for (j in seq_along(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering
    ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMismatchData)) {
  for (j in seq_along(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering
    ))
  }
}
```

```{r CPD_mismatch_type_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchTypeFrequencies(CPDMismatchData[[i]][[j]],
                                title = paste(c("CPD", titleCaseFiltering, names(CPDMismatchData)[i], 
                                                names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"),
                                              collapse = ' '))
  }
}
```

```{r 6-4_mismatch_type_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
                                title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
                                                names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"),
                                              collapse = ' '))
  }
}
```

```{r CPD_mismatch_pos_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste(c("CPD", titleCaseFiltering, names(CPDMismatchData)[i], 
                                                    names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"),
                                                  collapse = ' '))
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste(c("CPD", titleCaseFiltering, names(CPDMismatchData)[i], 
                                                    names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"),
                                                  collapse = ' '))
  }
}
```

```{r 6-4_mismatch_pos_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
                                                    names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"),
                                                  collapse = ' '))
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
                                                    names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"),
                                                  collapse = ' '))
  }
}
```

```{r CPD_trinucleotide_context_analysis}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotTrinucleotideContext(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                             title = paste(c("CPD", titleCaseFiltering, names(CPDMismatchData)[i],
                                             names(CPDMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
                                           collapse = ' '))
  }
}
```

```{r 6-4_trinucleotide_context_analysis}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotTrinucleotideContext(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                             title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i],
                                             names(sixFourMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
                                           collapse = ' '))
  }
}
```

```{r read_mismatch_frequency_z-score_tables}
CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}

sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMMFreqZScores)) {
  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}
```

```{r CPD_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = CPDMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = CPDMMFreqZScores$rep2)
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = CPDMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = CPDMMFreqZScores$rep2)
```

```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep2)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep2)
```

```{r CPD_read_length_distributions}
plotReadLengthFrequencies(CPDMismatchData$rep1,
                          title = paste(c("CPD", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
plotReadLengthFrequencies(CPDMismatchData$rep2,
                          title = paste(c("CPD", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
```

```{r 6-4_read_length_distributions}
plotReadLengthFrequencies(sixFourMismatchData$rep1,
                          title = paste(c("6-4", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
plotReadLengthFrequencies(sixFourMismatchData$rep2,
                          title = paste(c("6-4", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
```

```{r read_mismatch_position_statistics}
CPDGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                       rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    CPDGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
      strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering
    ))
  }
}

sixFourGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                           rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    sixFourGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
      strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering
    ))
  }
}
```

```{r CPD_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
                         xAxisBreaks = c(23:31))
plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
                         xAxisBreaks = c(23:31))
```

```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
                         xAxisBreaks = c(23:31))
plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
                         xAxisBreaks = c(23:31))
```
